Manuscript Figures for Genome Biology

### 2018-10-26 manuscript_figures/manuscript_figures_supp.Rmd
Fix error introduced in previous commit

# GSEA
resfile <- objects[grepl("GSEA", objects) & grepl("mouse", objects) & !grepl("uninf", objects)] 
res <- readRDS(file=resfile)
assayNames(res) <- "qvalue"
res <- addDefaultMetrics(res)
pC <- covariateLinePlot(res, alpha=alpha, covname="ind_covariate", trans="log1p",
                        nbins=25) +
  ggtitle("GSEA case study: Mouse") +
  xlab("Gene Set size percentile") + 
  theme(legend.position="none")

>>>>

# GSEA
resfile <- objects[grepl("GSEA", objects) & grepl("mouse", objects) & !grepl("uninf", objects)] 
res <- readRDS(file=resfile)
assayNames(res) <- "qvalue"
res <- addDefaultMetrics(res)
pC <- covariateLinePlot(res, alpha=alpha.thresh, covname="ind_covariate", trans="log1p",
                        nbins=25) +
  ggtitle("GSEA case study: Mouse") +
  xlab("Gene Set size percentile") + 
  theme(legend.position="none")
